
\chapter{LED Indication}

\newcommand{\LEDX}{{\rule{0.4em}{1.0em}}}
\newcommand{\LEDO}{{\rule{0.4em}{0.1em}}}

\newcommand{\ShowColor}[1]{{\color{#1}\rule{2em}{0.8em}}}

The device is equipped with five separate LED indicators that reflect either hardware or software status. 
Positions of LEDs on the board are shown on the figure \ref{fig:characteristics_leds_placement}.

\begin{itemize}
    \item \textbf{CAN1 and CAN2} green LEDs indicate data transfer through the CAN1 and CAN2 buses. 
           Blinks once if at least one CAN frame was successfully transmitted or successfully received in the last 
           25~ milliseconds. Glows steadily when the intensity of CAN traffic is higher than 40 frames per second.

    \item \textbf{ENABLE} orange LED indicates if the power transistor driver scheme is enabled.

    \item \textbf{GAIN} orange LED indicates the gain of motor currents measurement scheme. 
           If GAIN LED is ON, the gain is high for more accurate measurement at low power. 
           If GAIN LED is OFF, the gain is low  maintaining motor phase currents in measurement range. 
           Gain is switching automatically by firmware.

    \item \textbf{STATUS} RGB LED indicates the status of the firmware. 
          The behavior of the status LED is more complex than the other LEDs. 
          It is specified in the tables \ref{table:characteristics_status_led} 
          and \ref{table:characteristics_status_led_behavior}.
\end{itemize}

\begin{ZubaxSimpleTable}{Status LED during boot\label{table:characteristics_status_led}}{|l l X|}
    Color                     & Status                  & Description \\
    \ShowColor{yellow} Yellow & No application to boot  & The firmware haven't been 
    flashed to the ESC or FLASH has been damaged. \\
    \ShowColor{blue} Blue & Application upgrade is in progress. &   \\
    \ShowColor{green} Green & Boot canceled & The device firmware has not been properly signed. \\
    \ShowColor{magenta} Magenta   & Ready to boot & Glows after power up or restart the device 
    until the application starts.\\
\end{ZubaxSimpleTable}

\begin{ZubaxSimpleTable}{Status LED behavior\label{table:characteristics_status_led_behavior}}{|l X X|}
    LED pattern (step 80 ms) & Status & Description\\

    {\color{blue}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX} & Idle, ready to run & The ESC is ready and waiting for the setpoint.\\
    
    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDX\LEDX} & Idle, Hardware fault & The power stage is not ready or 
       current is tripped.\\

    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDO\LEDX\LEDX\LEDX} & Idle, Hardware test fault & The motor 
       is not connected or there is a short circuit on the output of the ESC.\\

    {\color{red}
       \LEDX\LEDO\LEDO\LEDO\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX\LEDO\LEDX
       \LEDX\LEDX\LEDO\LEDX\LEDX\LEDX} & Idle, Invalid motor parameters & Some motor parameters 
       are not properly initialized or the motor identification hasn't been performed.\\
\end{ZubaxSimpleTable}

